Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-06-06 EinC_Reponse.tex
EditorinChief Response: minor changes

\noindent xxx \ \ 
 We incorporated virtually all the recommended changes suggested by you, the associate editor, and the referees. 
We very much appreciate everyone's time and constructive comments. 
We believe the paper is significantly improved and the wording of the paper, compared to the Winter Simulation Conference paper, is changed as a result of the revision.
We also went through the paper and tried to change the text to reduce word for word copying. 
  \medskip

>>>>

\noindent  
We incorporated virtually all the recommended changes suggested by you, the associate editor, and the referees. 
We very much appreciate everyone's time and constructive comments. 
We believe the paper is significantly improved as a result. 
The wording of the paper, compared to the Winter Simulation Conference Proceedings version, is also changed as a result of the revision.
We also went through the paper and tried to change the text to reduce word for word copying. 
\medskip
